An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis

### 2021-08-04 analysis/preliminaryAnalysis.Rmd
Add n and prob by field

```{r load_processed_data}
# loads the processed data files output by the preprocessing performed above
load(here('data','processed','d_coding.rds'))
load(here('data','processed','lookup_external_guidance.rds'))
```

```{r load_functions}
# load custom functions
source(here('analysis','functions.R'))
```
Look at counts and proportions mentioning each topic. Use all journals (regardless of whether internal guidance is available) for denominator.
```{r tbl_counts_props}
d_coding %>%

  # Recode NAs to FALSE for internal guidance elements
  mutate(across(starts_with("has_") & (!contains("guidance")), ~replace_na(., FALSE) )) %>%

  select(starts_with("has_")) %>% 
  gtsummary::tbl_summary() %>%
  add_n() %>% 
  modify_footnote(everything() ~ NA)
```

@@

>>>>

```{r load_processed_data}
# loads the processed data files output by the preprocessing performed above
load(here('data','processed','d_coding.rds'))
load(here('data','processed','d_journals.rds'))
load(here('data','processed','lookup_external_guidance.rds'))
```

```{r load_functions}
# load custom functions
source(here('analysis','functions.R'))
```

```{r set_style_defaults}
theme_gtsummary_compact()
```
Look at counts and proportions mentioning each topic. Use all journals for denominator. Overall and by field.
``````{r tbl_counts_props}
d_journals %>% 
  select(journal, esi_field) %>% 
  left_join(d_coding, ., by = "journal") %>%

  # Recode NAs to FALSE
  mutate(across(
    everything()
    # starts_with("has_") & (!contains("guidance")) # for internal guidance elements
    , ~replace_na(., FALSE) )) %>%

  select(esi_field, starts_with("has_")) %>% 
  gtsummary::tbl_summary(
    by = esi_field,
      # statistic = list(everything() ~ "{p}% ({n} / {N})")
  ) %>%
  add_overall %>% 
  modify_footnote(everything() ~ NA) %>% 
  modify_caption("**Number and proportion of journals overall and by field providing internal statistical guidance by topic.** Denominator for all proportions is the number of journals in the field, regardless of whether the journal has internal guidance.")
```
Some initial observations
- Math and computer science are indeed at 0% across the board.
- Clinical medicine has 100% guidance. Also high in related field: biology & biochemistry, immunology, molecular bio & genetics. Also psych and neuro fields.

@@

External guidance types
```{r tbl_external_guidance_types}
lookup_external_guidance %>% 
  count(guidance_type) %>% 
  kable()
```
